### 2018-12-31 Sections/protocols_for_the_quantum_internet.tex
Minor formatting
Added authors to sections
Beamsplitter U

The simplest example to illustrate this is by considering the measurement of a single qubit,
\begin{align}
\ket\psi = \alpha\ket{0} + \beta\ket{1}.	
\end{align}
We begin by introducing an additional ancillary qubit in the logical $\ket{0}$ state, which we maximally entangle to the primary system with a CNOT gate. This yields two redundantly encoded qubits,
\begin{align}
\hat{\mathrm{CNOT}}\ket\psi \ket{0} = \alpha\ket{0}\ket{0} + \beta\ket{1}\ket{1},
\end{align}
characterised by the same amplitudes as the original qubit. The ancilla is then measured (destructively), which reads out the original state of the primary system to which it was correlated, but which has not been destroyed and may freely continue on its journey.

@@

Each individual beamsplitter in such a decomposition is an arbitrary $\mathrm{SU}(2)$ matrix acting on two photonic creation operators, $\hat{a}^\dag$ and $\hat{b}^\dag$,
\begin{align}\index{Beamsplitters}
\begin{pmatrix}
\hat{a}^\dag_\mathrm{out} \\
\hat{b}^\dag_\mathrm{out}
\end{pmatrix}=\begin{pmatrix}
U_{11} & U_{12} \\
U_{21} & U_{22}
\end{pmatrix}\begin{pmatrix}
\hat{a}^\dag_\mathrm{in} \\
\hat{b}^\dag_\mathrm{in}
\end{pmatrix}.
\end{align}
When operating in the polarisation basis, wave-plates\index{Wave-plates} enable the same transformation as beamsplitters do in dual-rail encoding. The phase-shifters implement the unitary operation,\index{Phase!Shifts}
\begin{align}
\hat\Phi(\phi)=e^{-i\phi\hat{n}},
\end{align}
or equivalently in the Heisenberg picture,
\begin{align}
\hat{U}\hat{a}^\dag\hat{U}^\dag \to e^{-i\phi}\hat{a}^\dag,
\end{align}
for phase-shift $\phi$.

These linear optics evolutions are most commonly implemented using either:
\begin{itemize}
\item Bulk optics: discrete optical elements are arranged on an optical table.\index{Bulk optics}
\item Time-bin architectures: time-bin encoded qubits (Sec.~\ref{sec:time_bin}) evolve through delay lines and interfere at a single central optical component.\index{Time-bin encoding}\index{Fibre-loops}
\item Integrated waveguides: all passive components are etched into a chip.\index{Waveguides}
\end{itemize}
These three main contenders are illustrated in Fig.~\ref{fig:LO_archs}.

@@

@@

>>>>

The simplest example to illustrate this is by considering the measurement of a single qubit,
\begin{align}
\ket\psi = \alpha\ket{0} + \beta\ket{1}.	
\end{align}
We begin by introducing an additional ancillary qubit in the logical $\ket{0}$ state, which we maximally entangle to the primary system with a CNOT gate. This yields two redundantly encoded\index{Redundant encoding} qubits,
\begin{align}
\hat{\mathrm{CNOT}}\ket\psi \ket{0} = \alpha\ket{0}\ket{0} + \beta\ket{1}\ket{1},
\end{align}
characterised by the same amplitudes as the original qubit. The ancilla is then measured (destructively), which reads out the original state of the primary system to which it was correlated, but which has not been destroyed and may freely continue on its journey.

@@

Each individual beamsplitter in such a decomposition is an arbitrary $\mathrm{SU}(2)$ matrix acting on two photonic creation operators, $\hat{a}^\dag$ and $\hat{b}^\dag$,
\begin{align}\index{Beamsplitters}
\begin{pmatrix}
\hat{a}^\dag_\mathrm{out} \\
\hat{b}^\dag_\mathrm{out}
\end{pmatrix}=\begin{pmatrix}
\sqrt{\eta} & \sqrt{1-\eta} \\
\sqrt{1-\eta} & -\sqrt{\eta}
\end{pmatrix}\begin{pmatrix}
\hat{a}^\dag_\mathrm{in} \\
\hat{b}^\dag_\mathrm{in}
\end{pmatrix},
\end{align}
\comment{Check this, where does phase go?}where $\eta$ is the beamsplitter's reflectivity, and $\phi$ is the phase relationship.

When operating in the polarisation basis, wave-plates\index{Wave-plates} enable the same transformation as beamsplitters do in dual-rail encoding. The phase-shifters implement the unitary operation,\index{Phase!Shifts}
\begin{align}
\hat\Phi(\phi)=e^{-i\phi\hat{n}},
\end{align}
or equivalently in the Heisenberg picture,
\begin{align}
\hat{U}\hat{a}^\dag\hat{U}^\dag \to e^{-i\phi}\hat{a}^\dag,
\end{align}
for phase-shift $\phi$.

These linear optics evolutions are most commonly implemented using either:
\begin{itemize}
\item Bulk optics: discrete optical elements are arranged on an optical table.\index{Bulk optics}
\item Time-bin architectures: time-bin encoded qubits (Sec.~\ref{sec:time_bin}) evolve through delay lines and interfere at a single central optical component.\index{Time-bin encoding}\index{Fibre-loops}
\item Integrated waveguides: all passive components are etched into a chip. When optical modes are brought physically close together, evanescent coupling\index{Evanescent coupling} allows photons to coherently hop between modes. This gives rise to evolution described by the coupled oscillator Hamiltonian\index{Coupled oscillator Hamiltonian}, given in Eq.~(\ref{eq:coupled_osc_ham}), where the coupling coefficients are dictated by the proximity and geometry of the waveguides.\index{Waveguides}
\end{itemize}
These three main contenders are illustrated in Fig.~\ref{fig:LO_archs}.

@@

\sectionby{Tim Byrnes}

@@

\sectionby{Zixin Huang}
